\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
More experimental results

J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We run J-ReCoVer on a virtual machine with 4GB of memeory running on a server with AMD Opteron 6376 CPU.The operation system is Ubuntu 16.04.5 LTS.

@@

J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories.
There is no other tool that could handle the reducers as they are. Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based backend verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool. Of course, in the future, this can be done if need be.

>>>>

J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We run J-ReCoVer on a virtual machine with 4GB of memeory running Ubuntu 16.04.5 LTS on a server with AMD Opteron 6376 CPU.

@@

\begin{wrapfigure}{r}{9cm}
	\begin{tabular}{|c|c|c|c||c|c|c|}
		\hline
		&Compile &Prepossesor &Prover & Lines & Variables & If-branches\\
		\hline
		Min. &6.22   &2.15        &0.032 & 5 & 4 & 0\\
		Avg. &6.54   &2.44        &0.046 & 20.5 & 14.7 & 1.2\\
		Max. &7.28   &3.06        &0.101 & 58 & 37 & 5\\
		\hline
	\end{tabular}
	\caption{Time in each step, size of the reducers}
\end{wrapfigure}  
For the $115$ solved cases, $72\%$ of the execution time are spent in compiling JAVA source code to bytecode, which is the input of the Soot tool. Another $27\%$ of the execution time are spent in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations. The time spent in Solver is quite limited, since the real-world integer reducer programs are usually not that big.

J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories.
There is no other tool that could handle the reducers as they are. Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool. Of course, in the future, this can be done if need be.
